\textit{Complex Variables and Elliptic Equations} \LaTeX\ guide for authors (Style 2 + NLM reference style)

### 2016-12-22 cvee_paper_gerasimovd.tex
Less macros

\newcommand{\mcO}{\mathcal{O}} % Big O
\newcommand{\iu}{{i\mkern1mu}} % imaginary unit
\newcommand{\eexp}[1]{e^{#1}}  % convenient exponent
\newcommand\abs[1]{\left|#1\right|}
\newcommand\norm[1]{\left\|#1\right\|}
\DeclareMathOperator\asin{asin}
\DeclareMathOperator\atanh{atanh}
\begin{document}

@@

\begin{itemize}
\item $\mathbb{C}$: complex plane, $\mathbb{C} = \{ x + \iu y \mid x, y \in \mathbb{R} \}$ 
\item $\mathbb{H}$: upper complex half-plane, $\mathbb{H} = \{ x + \iu y \mid y > 0, x, y \in \mathbb{R} \}$
\item $\mathbb{D}$: unit disk, $\mathbb{D} = \{ z \mid \abs{z} < 1 \}$
\item $\mathbb{T}$: unit circle, $\mathbb{T} = \partial \mathbb{D} =  \{z \mid \abs{z} = 1 \}$
\item $z$ denotes a complex argument on complex plane $\mathbb{C}$
\item $\zeta$ denotes a complex argument on unit disk $\mathbb{D}$
\end{itemize}

@@

Cayley transform maps $\mathbb{H}$ to $\mathbb{D}$:
\[
W(z) = \frac{z - \iu}{z + \iu}
\]
, whereas inverse Cayley transform maps $\mathbb{D}$ to $\mathbb{H}$:
\begin{equation}\label{eq:cayley_inverse}
w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}
\end{equation}

@@

Another important property we are going to use is that Cayley transform preserves circles. In particular, a circle with radius $0 < r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $\iu C(r)$ and radius $R(r)$, where:

@@

Also, we'll note two useful facts: TODO REFERENCE HERE FROM TEXT
\begin{itemize}
\item $C(r) - R(r) = \frac{(1 - r)^2}{1 - r^2} > 0$
\item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mcO(\frac{1}{R})$
\end{itemize}

@@

\begin{equation}\label{eq:wlwl}
\begin{aligned}
   \psi_L(x) &= A \eexp{\iu k x} + B \eexp{-\iu k x}
\\ \psi_R(x) &= C \eexp{\iu k x} + D \eexp{-\iu k x}
\end{aligned}
\end{equation}

@@

\begin{theorem}[{\cite[p. 95, 99]{nikol2012treatise}}]
The following statements are equivalent:
\begin{itemize}
\item the dissipating operator $Z$ is complete
\item
\begin{equation}\label{eq:blaschke}
\lim\limits_{r = 1} \int\limits_{\mathbb{T}} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
\end{equation}
\end{itemize}
\end{theorem}

We will use the criterion (\ref{eq:blaschke}) to analyze the completeness of the system of resonant states. In the space of the unit disk it looks like:
\begin{equation}\label{eq:crit_cayley}
\lim\limits_{r = 1} \int\limits_{\abs{\zeta} = r} \log \abs{\det S(\zeta)} d \zeta = 0
\end{equation}

@@

\begin{equation}\label{eq:crit}
\lim\limits_{r \to 1} \int\limits_{C_r} \ln \abs{\det S(k)} \frac{2 \iu}{(k + i)^2} dk = 0
\end{equation}
, where $C_r$ is an image of $\abs{\zeta} = r$ under the inverse Cayley transform (\ref{eq:cayley_inverse}). It can be parameterised as $C_r = \{R(r) \eexp{\iu t} + \iu C(r) \mid t \in [0, 2 \pi)\}$ (see \ref{eq:c_and_r}). For brevity, define:

\[
s(k) = \abs{\det S(k)}
\]
, and after throwing away constants which are irrelevant for convergence, we get the final form of the criterion, which is convenient for us and will be used afterwards:

\begin{equation}\label{eq:critp}
\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) \eexp{\iu t} + \iu C(r)) \frac{R}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} dt = 0
\end{equation}

@@

\begin{equation}\label{eq:bundle_s}
s(k) = \abs{\det S(k)} = \abs{\frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}}
\end{equation}

@@

To estimate, we need the Cauchy-Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]
, or to be precise, it's $\mathcal{L}^2[a, b]$ version:
\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}
\le
\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
\]
% 
To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
\begin{equation}\label{eq:split}
\begin{aligned}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{aligned}
\end{equation}
Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.

\subsection{Estimating $\norm{g}$}

First, we evaluate the integrand:
\begin{align*}
\abs{g(t)}^2 = \abs{g^*(t)}^2
&=   \frac{\sqrt{R}^2}{\abs{R \cos t + \iu R \sin t + \iu C + i}^2} \\
&=   \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} \\
&= \frac{R}{R^2 \cos^2 t + R^2 \sin^2 t + (C + 1)^2  + 2 R (C + 1) \sin t} \\
&=   \frac{1}{R + \frac{(C + 1)^2}{R} + 2 (C + 1) \sin t} \\ 
\end{align*}

@@

Finally, since $\frac{2 \pi}{\sqrt{a^2 - b^2}} \le \frac{2 \pi}{2} = \pi$, and we just proved that $\norm{g}$ is bounded by a constant.

\subsection{Estimating $\norm{f}$}
Function $s(k)$ (\ref{eq:bundle_s}) is too complex for direct proof of the convergence.

@@

\begin{enumerate}
\item
  It is easy to spot that if we fix the complex part of the argument, $s(k)$ is periodic with respect to the real part of its argument.
\item 
  Function $s(k)$ has countably infinite set of zeros, and each of them has $\operatorname{Im} k = \atanh \frac{2 W}{W^2 + 1}$. For brevity, we define:

  \begin{equation*}
  \begin{aligned}
     V &= \frac{2 W}{W^2 + 1}
  \\ Z &= \atanh V
  \end{aligned}
  \end{equation*}
\item
  Notice that for each $x$, $s(x + \iu y) \le s(\iu y)$.
\end{enumerate}

Given these facts, we can build a simple lower bound for $s(x + \iu y)$:
\begin{align*}
l(x + \iu y)
   &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}}
\\ &= \abs{\frac{\tanh y - V}{\tanh y + V}} && \text{(since $\cosh y > 0$)}
\end{align*}

It's pretty clear that $l(k)$ has a continuum of zeros over the line $\operatorname{Im} k = Z$, which implies that $\ln l(k)$ has continuum number of singularities over this line. Intuitively, it shouldn't spoil the convergence of integral since the contour of integration could intersect the singularities of the original function anyway. And indeed, we will give a rigorous argument that we still can prove convergence in this case. Since the function is independent from the real part of the argument now, for brevity, we will omit it and define $l(y) = l(\iu y)$.

Now, we will simplify the integral using the bound we just constructed:
\begin{align*}
       \int\limits_{t=0}^{2 \pi} \abs{f(t)}^2 dt
   = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \eexp{\iu t} + \iu C) \frac{R}{\norm{R \eexp{\iu t} + \iu C + i}^2} dt
\\ = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt
\end{align*}

@@

Next, we do a variable change:
\begin{equation*}
\begin{aligned}
   y         &= R \sin t + C
\\ t         &= \asin \frac{y - C}{R}
\\ dt        &= \frac{1}{\sqrt{R^2 - (C - y)^2}} dy
\\ \cos t    &= \frac{\sqrt{R^2 - (C - y)^2}}{R}
\\ y(-\pi/2) &= C - R 
\\ y(\pi/2)  &= C + R 
\end{aligned}
\end{equation*}
, and after substitution:
\begin{equation}\label{eq:int_f}
\resizebox{0.9\hsize}{!}{$
\begin{aligned}
    & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}  dy\\
\end{aligned}
$}
\end{equation}

@@

It's clear that the multiplier before the integral has order $\mcO(\sqrt{R})$ (we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$).

@@

This implies that we can estimate the function from above by using its value on the rightmost point of the interval at $\frac{V}{4}$.
\[
\frac{y^2}{a + b y} \le \frac{\frac{V^2}{16}}{R^2 - C^2 + 1 + 2 (C + 1) \frac{V}{4}} = \mcO\left(\frac{1}{R}\right)
\]

Integral of the second part of the integrand is:
\[
\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mcO(1)
\]

And finally, after combining we get $\mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$.

@@

First, take a look at the multiplier before the integral, it's pretty clear it has order of growth $\mcO(\frac{1}{\sqrt{R}})$.

@@

In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$, hence the integral on this interval grows as $\mcO(\frac{1}{\sqrt{R}})$.

\subsubsection{Case 2: $y > Z$}
When $y > Z$, 
\[
l(x + \iu y) 
 = \frac{\tanh y - V}{\tanh y + V}
 = 1 - 2 \frac{V}{\tanh y + V}
\]

@@

It's easy to see that the coefficient before the integral has order of growth $\mcO\left(\frac{1}{\sqrt{R}}\right)$.

@@

Hence, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) + 2)$. As we noted above, $l(C + R)$ is bounded by positive constants less than $1$ and independent of $r$, and we can see that the expression grows as $\mcO(\frac{\ln^2 R}{R})$.

By combining the estimates for the coefficient and the integral, we get $\mcO(\frac{\ln^2 R}{R \sqrt{R}})$.

@@

As $R$ goes to infinity, $\ln^2 f(Z + \frac{1}{R})$ goes to infinity as well, so we have to compute the order of singularity. Since $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, we can see that $\ln^2 f(Z + \frac{1}{R}) = \mcO (\ln^2 R)$.

As for the integral, antiderivative for such a function is well known:
\[
\int \frac{1}{a x + b} = \frac{\ln (a x + b)}{a}
\]
, in our case $a = 2 (C + 1)$, $b = R^2 - C^2 + 1$. Substituting the ends of the interval $(Z + \frac{1}{R}, C)$, we get the definite integral:
\[
\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \mcO\left( \frac{\ln R}{R} \right)
\]

Finally, after combining, we get: $\mcO (\ln^2 R) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} \mcO\left( \frac{\ln R}{R} \right)  = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)$.

@@

Again, estimating \ref{eq:int_f_up} from above:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
% \\  = & \ln^2 f(y) \mcO()
\end{align*}

Integral $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is elementary and equals $2 \sqrt{R}$. Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm as well. Finally, we get an expression of order $\mcO \left( \frac{1}{R} \right) \mcO( \sqrt R ) = \mcO \left( \frac{1}{\sqrt{R}} \right)$.

\subsubsection{Final estimate of $\int \abs{f(t)}^2$}
We split our integration path in five intervals, and the integral has order:
\[
\mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) +\mcO\left(\frac{\ln^2 R}{R \sqrt{R}}\right) + \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)
\]
, which means that integral converges to $0$ as $r$ goes to $1$ and $R$ goes to $\infty$.

>>>>

\begin{document}

@@

\begin{itemize}
\item $\mathbb{C}$: complex plane, $\mathbb{C} = \{ x + \mathrm{i} y \mid x, y \in \mathbb{R} \}$ 
\item $\mathbb{H}$: upper complex half-plane, $\mathbb{H} = \{ x + \mathrm{i} y \mid y > 0, x, y \in \mathbb{R} \}$
\item $\mathbb{D}$: unit disk, $\mathbb{D} = \{ z \mid \left|z\right| < 1 \}$
\item $\mathbb{T}$: unit circle, $\mathbb{T} = \partial \mathbb{D} =  \{z \mid \left|z\right| = 1 \}$
\item $z$ denotes a complex argument on complex plane $\mathbb{C}$
\item $\zeta$ denotes a complex argument on unit disk $\mathbb{D}$
\end{itemize}

@@

Cayley transform maps $\mathbb{H}$ to $\mathbb{D}$:
\[
W(z) = \frac{z - \mathrm{i}}{z + \mathrm{i}}
\]
, whereas inverse Cayley transform maps $\mathbb{D}$ to $\mathbb{H}$:
\begin{equation}\label{eq:cayley_inverse}
w(\zeta) = \mathrm{i} \frac{1 + \zeta}{1 - \zeta}
\end{equation}

@@

Another important property we are going to use is that Cayley transform preserves circles. In particular, a circle with radius $0 < r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $\mathrm{i} C(r)$ and radius $R(r)$, where:

@@

Also, we'll note two useful facts: TODO REFERENCE HERE FROM TEXT
\begin{itemize}
\item $C(r) - R(r) = \frac{(1 - r)^2}{1 - r^2} > 0$
\item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mathcal{O}(\frac{1}{R})$
\end{itemize}

@@

\begin{equation}\label{eq:wlwl}
\begin{aligned}
   \psi_L(x) &= A e^{\mathrm{i} k x} + B e^{-\mathrm{i} k x}
\\ \psi_R(x) &= C e^{\mathrm{i} k x} + D e^{-\mathrm{i} k x}
\end{aligned}
\end{equation}

@@

\begin{theorem}[{\cite[p. 95, 99]{nikol2012treatise}}]
The following statements are equivalent:
\begin{itemize}
\item the dissipating operator $Z$ is complete
\item
\begin{equation}\label{eq:blaschke}
\lim\limits_{r = 1} \int\limits_{\mathbb{T}} \log \left|\det S(r \zeta)\right| d m(\zeta) = 0
\end{equation}
\end{itemize}
\end{theorem}

We will use the criterion (\ref{eq:blaschke}) to analyze the completeness of the system of resonant states. In the space of the unit disk it looks like:
\begin{equation}\label{eq:crit_cayley}
\lim\limits_{r = 1} \int\limits_{\left|\zeta\right| = r} \log \left|\det S(\zeta)\right| d \zeta = 0
\end{equation}

@@

\begin{equation}\label{eq:crit}
\lim\limits_{r \to 1} \int\limits_{C_r} \ln \left|\det S(k)\right| \frac{2 \mathrm{i}}{(k + i)^2} dk = 0
\end{equation}
, where $C_r$ is an image of $\left|\zeta\right| = r$ under the inverse Cayley transform (\ref{eq:cayley_inverse}). It can be parameterised as $C_r = \{R(r) e^{\mathrm{i} t} + \mathrm{i} C(r) \mid t \in [0, 2 \pi)\}$ (see \ref{eq:c_and_r}). For brevity, define:

\[
s(k) = \left|\det S(k)\right|
\]
, and after throwing away constants which are irrelevant for convergence, we get the final form of the criterion, which is convenient for us and will be used afterwards:

\begin{equation}\label{eq:critp}
\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) e^{\mathrm{i} t} + \mathrm{i} C(r)) \frac{R}{(R(r) e^{\mathrm{i} t} + \mathrm{i} C(r) + i)^2} dt = 0
\end{equation}

@@

\begin{equation}\label{eq:bundle_s}
s(k) = \left|\det S(k)\right| = \left|\frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}\right|
\end{equation}

@@

To estimate, we need the Cauchy-Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]
, or to be precise, it's $\mathcal{L}^2[a, b]$ version:
\[
\left|
\int\limits_{t=a}^{b} f(t) g^*(t) dt
\right|
\le
\sqrt{\int\limits_{t=a}^b \left|f(t)\right|^2 dt }
\sqrt{\int\limits_{t=a}^b \left|g(t)\right|^2 dt }
\]
% 
To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
\begin{equation}\label{eq:split}
\begin{aligned}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R e^{\mathrm{i} t} + \mathrm{i} C) \frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i}
\end{aligned}
\end{equation}
Next, we will show that $\|g\|$ (that is, $\sqrt{\int \left|g(t)\right|^2}$) is bounded by a constant which does not depend on $r$, and $\|f\|$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.

\subsection{Estimating $\|g\|$}

First, we evaluate the integrand:
\begin{align*}
\left|g(t)\right|^2 = \left|g^*(t)\right|^2
&=   \frac{\sqrt{R}^2}{\left|R \cos t + \mathrm{i} R \sin t + \mathrm{i} C + i\right|^2} \\
&=   \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} \\
&= \frac{R}{R^2 \cos^2 t + R^2 \sin^2 t + (C + 1)^2  + 2 R (C + 1) \sin t} \\
&=   \frac{1}{R + \frac{(C + 1)^2}{R} + 2 (C + 1) \sin t} \\ 
\end{align*}

@@

Finally, since $\frac{2 \pi}{\sqrt{a^2 - b^2}} \le \frac{2 \pi}{2} = \pi$, and we just proved that $\|g\|$ is bounded by a constant.

\subsection{Estimating $\|f\|$}
Function $s(k)$ (\ref{eq:bundle_s}) is too complex for direct proof of the convergence.

@@

\begin{enumerate}
\item
  It is easy to spot that if we fix the complex part of the argument, $s(k)$ is periodic with respect to the real part of its argument.
\item 
  Function $s(k)$ has countably infinite set of zeros, and each of them has $\operatorname{Im} k = \operatorname{arctanh} \frac{2 W}{W^2 + 1}$. For brevity, we define:

  \begin{equation*}
  \begin{aligned}
     V &= \frac{2 W}{W^2 + 1}
  \\ Z &= \operatorname{arctanh} V
  \end{aligned}
  \end{equation*}
\item
  Notice that for each $x$, $s(x + \mathrm{i} y) \le s(\mathrm{i} y)$.
\end{enumerate}

Given these facts, we can build a simple lower bound for $s(x + \mathrm{i} y)$:
\begin{align*}
l(x + \mathrm{i} y)
   &= \left|\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}\right|
\\ &= \left|\frac{\tanh y - V}{\tanh y + V}\right| && \text{(since $\cosh y > 0$)}
\end{align*}

It's pretty clear that $l(k)$ has a continuum of zeros over the line $\operatorname{Im} k = Z$, which implies that $\ln l(k)$ has continuum number of singularities over this line. Intuitively, it shouldn't spoil the convergence of integral since the contour of integration could intersect the singularities of the original function anyway. And indeed, we will give a rigorous argument that we still can prove convergence in this case. Since the function is independent from the real part of the argument now, for brevity, we will omit it and define $l(y) = l(\mathrm{i} y)$.

Now, we will simplify the integral using the bound we just constructed:
\begin{align*}
       \int\limits_{t=0}^{2 \pi} \left|f(t)\right|^2 dt
   = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R e^{\mathrm{i} t} + \mathrm{i} C) \frac{R}{\|R e^{\mathrm{i} t} + \mathrm{i} C + i\|^2} dt
\\ = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt
\end{align*}

@@

Next, we do a variable change:
\begin{equation*}
\begin{aligned}
   y         &= R \sin t + C
\\ t         &= \arcsin \frac{y - C}{R}
\\ dt        &= \frac{1}{\sqrt{R^2 - (C - y)^2}} dy
\\ \cos t    &= \frac{\sqrt{R^2 - (C - y)^2}}{R}
\\ y(-\pi/2) &= C - R 
\\ y(\pi/2)  &= C + R 
\end{aligned}
\end{equation*}
, and after substitution:
\begin{equation}\label{eq:int_f}
\resizebox{0.9\hsize}{!}{$
\begin{aligned}
    & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}  dy\\
\end{aligned}
$}
\end{equation}

@@

It's clear that the multiplier before the integral has order $\mathcal{O}(\sqrt{R})$ (we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$).

@@

This implies that we can estimate the function from above by using its value on the rightmost point of the interval at $\frac{V}{4}$.
\[
\frac{y^2}{a + b y} \le \frac{\frac{V^2}{16}}{R^2 - C^2 + 1 + 2 (C + 1) \frac{V}{4}} = \mathcal{O}\left(\frac{1}{R}\right)
\]

Integral of the second part of the integrand is:
\[
\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mathcal{O}(1)
\]

And finally, after combining we get $\mathcal{O}(\sqrt{R}) \mathcal{O}\left(\frac{1}{R}\right) \mathcal{O}(1)  = \mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.

@@

First, take a look at the multiplier before the integral, it's pretty clear it has order of growth $\mathcal{O}(\frac{1}{\sqrt{R}})$.

@@

In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$, hence the integral on this interval grows as $\mathcal{O}(\frac{1}{\sqrt{R}})$.

\subsubsection{Case 2: $y > Z$}
When $y > Z$, 
\[
l(x + \mathrm{i} y) 
 = \frac{\tanh y - V}{\tanh y + V}
 = 1 - 2 \frac{V}{\tanh y + V}
\]

@@

It's easy to see that the coefficient before the integral has order of growth $\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.

@@

Hence, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) + 2)$. As we noted above, $l(C + R)$ is bounded by positive constants less than $1$ and independent of $r$, and we can see that the expression grows as $\mathcal{O}(\frac{\ln^2 R}{R})$.

By combining the estimates for the coefficient and the integral, we get $\mathcal{O}(\frac{\ln^2 R}{R \sqrt{R}})$.

@@

As $R$ goes to infinity, $\ln^2 f(Z + \frac{1}{R})$ goes to infinity as well, so we have to compute the order of singularity. Since $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, we can see that $\ln^2 f(Z + \frac{1}{R}) = \mathcal{O} (\ln^2 R)$.

As for the integral, antiderivative for such a function is well known:
\[
\int \frac{1}{a x + b} = \frac{\ln (a x + b)}{a}
\]
, in our case $a = 2 (C + 1)$, $b = R^2 - C^2 + 1$. Substituting the ends of the interval $(Z + \frac{1}{R}, C)$, we get the definite integral:
\[
\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \mathcal{O}\left( \frac{\ln R}{R} \right)
\]

Finally, after combining, we get: $\mathcal{O} (\ln^2 R) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} \mathcal{O}\left( \frac{\ln R}{R} \right)  = \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right)$.

@@

Again, estimating \ref{eq:int_f_up} from above:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
% \\  = & \ln^2 f(y) \mathcal{O}()
\end{align*}

Integral $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is elementary and equals $2 \sqrt{R}$. Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm as well. Finally, we get an expression of order $\mathcal{O} \left( \frac{1}{R} \right) \mathcal{O}( \sqrt R ) = \mathcal{O} \left( \frac{1}{\sqrt{R}} \right)$.

\subsubsection{Final estimate of $\int \left|f(t)\right|^2$}
We split our integration path in five intervals, and the integral has order:
\[
\mathcal{O} \left( \frac{1}{\sqrt{R}} \right) + \mathcal{O} \left( \frac{1}{\sqrt{R}} \right) +\mathcal{O}\left(\frac{\ln^2 R}{R \sqrt{R}}\right) + \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mathcal{O} \left( \frac{1}{\sqrt{R}} \right) = \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right)
\]
, which means that integral converges to $0$ as $r$ goes to $1$ and $R$ goes to $\infty$.
